Methodology for Assessing the State of the Practice for Domain X

### 2020-09-20 StateOfPractice/Methodology/Methodology.tex
updated section 6 of Methodology doc

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software should be filtered using the following properties:
\begin{enumerate}
	\item Organization - The software and any related documentation should appear to be easy to gather and understand.
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\ad{What if installation or usage procedures are unavailable? I think we're measuring that if the software have installation instructions and user manuals,
	so perhaps they should be kept even if these docs are missing.}
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
	\item \ad{What if there are still more candidates than we need? Should we also filter out the ``older'' or ``less popular'' ones if needed? }
\end{enumerate}

>>>>

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software packages should first be filtered to a manageable size. Our target is about 30 packages. We want the list to include packages that are not marked as incomplete and are at least somewhat organized and understandable. We also want the list to be a good representation of the software domain, with packages having enough in common with respect to functionality that it makes sense to compare the software. The initial list of candidate software should be filtered using the following properties:

\begin{enumerate}
	\item Organization - The software and any related documentation should appear to be easy to gather and understand.
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\ad{What if installation or usage procedures are unavailable? I think we're measuring that if the software have installation instructions and user manuals,
	so perhaps they should be kept even if these docs are missing.}
    \pmi{How are we installing the software if such documents and procedures are missing? Should we expect users to be able to install? I did not encounter a situation where even basic installation steps were missing.}
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
	\item \ad{What if there are still more candidates than we need? Should we also filter out the ``older'' or ``less popular'' ones if needed? }\pmi{Good question. Let's discuss during meeting.}
\end{enumerate}
